Compositional equivalences based on Open pNets

### 2021-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
changed end of conclusion (tools et work in progress)
manque encore refbib "SMC"

We are currently extending this work,  looking at further properties of FH-bisimulation, but also
the relations with existing equivalences on both closed and open systems. In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
would be interesting to compare our "FH" family of bisimulations with the hierarchy of symbolic bisimulations from these authors.
We also plan to apply open pNets to the study of complex composition
operators in a symbolic way, for example in the area of parallel
skeletons, or distributed algorithms.
We have developed tool support for computing the
symbolic semantics in term of open automata \cite{QBMZ-AVOCS18}, and have
developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.  
Naturally we are now working toward an implementation of weak FH-Bisimulation. 
The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
as was the case with classical weak bisimulation on finite models, but decidability and termination.
Two main directions should be explored, either with an explicit construction of the weak transition, but this step in
itself may introduce non-termination, or a direct implementation of the weak bisimulation definition, without
constructing the weak automaton. We can expect that optimisations here in the symbolic setting would be quite different from the classical case.

>>>>

We are currently extending this work,  looking at further properties of FH-bisimulation, but also
the relations with existing equivalences on both closed and open systems. In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
would be interesting to compare our "FH" family of bisimulations with the hierarchy of symbolic bisimulations from these authors.
We also plan to apply open pNets to the study of complex composition
operators in a symbolic way, for example in the area of parallel
skeletons, or distributed algorithms.
We have developed tool support for computing the
symbolic semantics in term of open automata \cite{QBMZ-AVOCS18}, and have
developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.
More reecntly we published preliminary work for the case of weak FH-Bisimulation \cite{}. 
The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
as was the case with classical weak bisimulation on finite models, but decidability and termination.
The naive approach using an explicit construction of the weak transition, may in itself introduce non-termination,
so we prefer a direct implementation of the weak bisimulation definition, without
constructing the weak automaton, but searching \emph{on demand} to construct the required weak transitions.
Alternatively, we explore more pragmatic approaches using weak bisimulation preserving (pattern-based) 
reduction rules \cite{wang:hal-03126313}.
